The fraction of polar aligned circumbinary disks

### 2025-04-04 src/tex/ms.tex
Set up for review
L642

\newcommand{\TJ}[1]{\textcolor{orange}{#1}}
\newcommand{\RGM}[1]{\textcolor{cyan}{#1}}

@@

Observed circumbinary planets -- those orbiting two stars -- have mostly been found to orbit in the same plane as their hosts \citep{doyle2011,orosz2012,welsh2012}. While this preference is the result of target selection effects (\citealt{martin2014}, see also \citealt{martin2015}, \citealt{martin2017a}), it is also representative of the fact that, for the disk progenitors of these planets \citep[from which the planets inherit orbital parameters, see][]{childs2021}, a coplanar alignment is one of two possible stable orientations \citep{bate2000,lubow2000}. The other configuration -- a polar disk -- is characterized by being inclined $90^\circ$ relative to the binary orbital plane \citep{aly2015,martin2017}. Evidence for one polar planet has been found via indirect means \citep[AC Her, ][]{hillen2015,anugu2023,martin2023}, and only a handful of confirmed polar disks have ever been discovered. These include a polar debris disk in the 99 Her system (\citealt{kennedy2012}, which likely evolved from a polar gas disk, see \citealt{smallwood2020}) and polar gas disks in the HD 98800 \citep{kennedy2019} and V773 Tau \citep{kenworthy2022} systems.

@@

We also discuss the limitations of our methods. First, we look at the effect of finite disk lifetime on the ability for a disk to complete its evolution to a stationary state. Disks with long evolutionary timescales remain with orbital parameters near their initial conditions for their entire lifetimes. We also look at limitations imposed by the fact that real disks are not geometrically narrow rings, but have some radial extent. Real disks are likely to break if their radial extent is too large, and will become gravitationally unstable if all of their mass in concentrated in too narrow of a ring. These two effects impose constraints on the relationship between $r_\text{in}$, $r_\text{out}$, and $j$.

>>>>

\newcommand{\TJ}[1]{\textcolor{orange}{#1}}
\newcommand{\RGM}[1]{\textcolor{cyan}{#1}}
\newcommand{\RR}[1]{\textcolor{blue}{\bf#1}} % reviewer's report

@@

Observed circumbinary planets -- those orbiting two stars -- have mostly been found to orbit in the same plane as their hosts \citep{doyle2011,orosz2012,welsh2012}. While this preference is the result of target selection effects (\citealt{martin2014}, see also \citealt{martin2015}, \citealt{martin2017a}), it is also representative of the fact that, for the disk progenitors of these planets \citep[from which the planets inherit orbital parameters, see][]{childs2021}, a coplanar alignment is one of two possible stable orientations \citep{bate2000,lubow2000}. The other configuration -- a polar disk -- is characterized by being inclined $90^\circ$ relative to the binary orbital plane \citep{aly2015,martin2017}. \RR{O}nly a handful of confirmed polar disks have ever been discovered. These include a polar debris disk in the 99 Her system (\citealt{kennedy2012}, which likely evolved from a polar gas disk, see \citealt{smallwood2020}) and polar gas disks in the HD 98800 \citep{kennedy2019} and V773 Tau \citep{kenworthy2022} systems. \RR{Evidence for one polar planet has been found via indirect means \citep[AC Her, ][]{hillen2015,anugu2023,martin2023}}

@@

We also discuss the limitations of our methods. First, we look at the effect of finite disk lifetime on the ability for a disk to complete its evolution to a stationary state. Disks with long evolutionary timescales remain with orbital parameters near their initial conditions for their entire lifetimes. We also look at limitations imposed by the fact that real disks are not geometrically narrow rings, but have some radial extent. Real disks are likely to break if their radial extent is too large, and will become gravitationally unstable if all of their mass in concentrated in too narrow of a ring. These two effects impose constraints on the relationship between $r_\text{in}$, $r_\text{out}$, and $j$.
\RR{
These results for $f_\text{polar}$ can be tested through population-level observations of circumbinary disk systems. In practice, however, the mutual inclination between the disk and its binary host can be difficult to constrain, and therefore polar disks can be difficult to distinguish from coplanar. Known misaligned disks rely on fortunate geometry to constrain the mutual inclination, such as an eclipse of a nearby binary in the case of V773 Tau B \citep{kenworthy2022}. However, $f_\text{polar}$ could be statistically constrained by looking for polar disks around young eclipsing binaries because the binary-observer inclination is known. Imaging of a face-on disk in such systems would confirm a polar configuration. However, for an edge-on disk it would be difficult to differentiate between a coplanar and polar due to a degeneracy in viewing angle. A carefully done survey of a large population of eclipsing binaries \citep[e.g., those found by the Kepler Mission][]{kirk2016} would likely constrain the fraction of polar circumbinary disks.
}

### 2025-04-04 src/tex/review.tex
L642

\newenvironment{response}[1]{
    \fcolorbox{blue}{white}{
    \begin{minipage}{0.4\textwidth}
        #1
    \end{minipage}
    }
    \begin{minipage}{0.4\textwidth}
    }
    {\end{minipage}}

@@

>>>>

\newenvironment{response}[1]{
    \fcolorbox{blue}{white}{
    \begin{minipage}{0.46\textwidth}
        #1
    \end{minipage}
    }\hfill
    \begin{minipage}{0.46\textwidth}
    }
    {\end{minipage}}

@@

    \begin{response}{
        L642: At the end of the conclusions (or else at the end of the discussion), a brief discussion on how future observations could test these findings would add value to the article.
    }
        We have added a discussion about the possibility of confirming this work though observations. We propose a survey to measure the inclinations of disks in young eclipsing binary systems could reasonably constrain the polar fraction.
    \end{response}
